% David Tyler's Resume
% Created: 03/03/2014
% Last Modified:  03/03/2014

\documentclass[10pt,oneside]{article}
\usepackage{geometry}
\usepackage[T1]{fontenc}

\pagestyle{empty}
\geometry{letterpaper,tmargin=0.5in,bmargin=0.5in,lmargin=0.5in,rmargin=0.5in,headheight=0in,headsep=0in,footskip=.3in}

\setlength{\parindent}{0in}
\setlength{\parskip}{0in}
\setlength{\itemsep}{0in}
\setlength{\topsep}{0in}
\setlength{\tabcolsep}{0in}

% Name and contact information
\newcommand{\name}{David Tyler}
\newcommand{\addr}{41 Mason St}
\newcommand{\addrs}{Somerville, MA 02144}
\newcommand{\phone}{978-212-9199}
\newcommand{\email}{dtyler59@gmail.com}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% New commands and environments

% This defines how the name looks
\newcommand{\bigname}[1]{
	\begin{center}\fontfamily{phv}\selectfont\huge\scshape#1\end{center}
}

% A ressection is a main section (<H1>Section</H1>)
\newenvironment{ressection}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}
	\begin{itemize}
	\vspace{3pt}
}{
	\end{itemize}
}

%same as ressection but without bullets
\newenvironment{ressectionplain}[1]{
	\vspace{4pt}
	{\fontfamily{phv}\selectfont\Large#1}\\
}


% A resitem is a simple list element in a ressection (first level)
\newcommand{\resitem}[1]{
	\vspace{-4pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A ressubitem is a simple list element in anything but a ressection (second level)
\newcommand{\ressubitem}[1]{
	\vspace{-1pt}
	\item \begin{flushleft} #1 \end{flushleft}
}

% A resbigitem is a complex list element for stuff like jobs and education:
%  Arg 1: Name of company or university
%  Arg 2: Location
%  Arg 3: Title and/or date range
\newcommand{\resbigitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3}
}
%Places GPA on same line as degree
\newcommand{\resbigitemdegrees}[4]{
	\vspace{-5pt}
	\item
	\textbf{#1}---#2 \\
	\textit{#3} #4
}

%Same as resbigitem but without the hyphenation
\newcommand{\ressmallitem}[3]{
	\vspace{-5pt}
	\item
	\textbf{#1} {#2}\\
	\textit{#3}
}

% This is a list that comes with a resbigitem
\newenvironment{ressubsec}[3]{
	\resbigitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}
%Same as ressubsec but without bullets
%\newenvironment{ressubsecplain}[3]{  
%	\resbigitem{#1}{#2}{#3}
%	\vspace{-2pt} \\
%}
%Same as ressubsec but without hyphenation
\newenvironment{ressubsecsmall}[3]{
	\ressmallitem{#1}{#2}{#3}
	\vspace{-2pt}
	\begin{itemize}
}{
	\end{itemize}
}

%Same as ressubsec but another set of fields
\newenvironment{ressubsecdegrees}[4]{
	\resbigitemdegrees{#1}{#2}{#3}{#4}
	\vspace{-2pt}
%	\begin{itemize}
}%{
%
%	\end{itemize}
%}

% This is a simple sublist
\newenvironment{reslist}[1]{
	\resitem{\textbf{#1}}
	\vspace{-5pt}
	\begin{itemize}
}{
	\end{itemize}
}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Now for the actual document:

\begin{document}

\fontfamily{ppl} \selectfont

% Name with horizontal rule
\bigname{\name}


\vspace{-1pt} {\small \addr \hfill \phone}\\
\vspace{-1pt}{\small \addrs \hfill \email}

\vspace{-8pt} \rule{\textwidth}{1pt}


\vspace{8 pt}




%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressectionplain}{Summary}

Inquisitive Computer Engineer with industry design and test experience in both the hardware and software, strong collaboration experience, and excellent communications skills. Graduating this fall and currently looking for a summer internship.\newline


%Independently motivated Electrical Engineer with a background in theory, computation, and application and strong multitasking, planning, and communication skills.\newline

%ENGINEERING:
%Motivated Electrical Engineer with experience in computation and fabrication and strong\\ multitasking, planning, and communication skills seeking a career in the Semiconductor Industry.\\ %actively involved in engineering and outreach organizations%

%EDUCATION RESEARCH CHILDREN
%Responsible and motivated Electrical Engineer with strong communication and research skills with experience designing and teaching courses in Robotics, Computer Technology, and Engineering for elementary through college students.\newline

%ENGINEERING EDUCATION ADMIN
%Responsible and motivated Electrical Engineer with strong communication and planning skills and industry and academia experience, seeking to start a career in engineering education.
\end{ressectionplain}
%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{ressection}{Industry Experience}

\begin{ressubsec}{Clark Solutions}{Hudson, MA \hfill 2014-Present}
{Junior Engineer}
\ressubitem{Designed, wrote, tested, and shipped a GUI application to allow customers to configure an ultrasonic flowmeter over a MODBUS RTU network from their PC.}
\ressubitem{Ported entire company's codebase from HI-TECH compiler to XC8 compiler.}
\ressubitem{Debugged ''spaghetti'' code written for a PIC16F886 and refactored it.}
\ressubitem{Implemented source control for all software maintained by company in addition to creating an entire set of QA procedures in order to address product quality issues.}
\end{ressubsec}

\begin{ressubsec}{Clark Solutions}{Hudson, MA \hfill 2009-2012}
{Technician}
\ressubitem{Assisted in the design process to build and test new ultrasonic flow meters.}
\ressubitem{Built, tested, and repaired ultrasonic flowmeters.}
\ressubitem{Made software fixes to flowmeter codebase and supporting programs.}
%\ressubitem{Did minor IT work including virus removal, database migration from oracle to mssql, creation of norton ghost images.}

\end{ressubsec}


\end{ressection}

\begin{ressection}{Academic Experience}

\begin{reslist}{Capstone Project}
\ressubitem{In the process of creating a puzzle game to teach children the basics of logic design and CMOS using physical interconnectable blocks.}
\end{reslist}

\begin{reslist}{Real Time Embedded Operating Systems}
\ressubitem{Used the Micrum microC/OS-III RTOS on the STM32F107 microcontroller to implement a command and control system for networked robots.}
\end{reslist}

\begin{reslist}{Microprocessors II}
\ressubitem{Project leader to use a PIC microcontroller to record timestamped light intensity measurements and report it to a webserver using a custom linux kernel driver.}
\end{reslist}

\begin{reslist}{Embedded Control}
\ressubitem{Worked with a group to design, build, and program a blimp for autonomous operation}
\end{reslist}

\end{ressection}


%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{ressection}{Education}

	
\begin{ressubsecdegrees}{University of Massachusetts Lowell}{Lowell, MA \hfill Expected Graduation: December 2014}{B.S. in Computer Engineering}{\hfill GPA: 3.5}
\end{ressubsecdegrees}		
	
\begin{ressubsecdegrees}{Rensselaer Polytechnic Institute}{Troy, NY \hfill 2006-2008}{Enrolled in Computer Engineering}{}
			%\ressubitem{Minor in Mathematics}
			%\ressubitem{GPA: 3.46}
		\end{ressubsecdegrees}		

\end{ressection}
	

%%%%%%%%%%%%%%%%%%%%%%%%
\begin{ressection}{Skills}
	\resitem{\textbf{Programming Languages:} C, C++, Python, LISP, SQL, MIPS, x86, PIC16, MSP430l}
	\resitem{\textbf{Operating Systems:} Microsoft Windows, Linux (Arch, Slax), OS X}
	\resitem{\textbf{Tools:} vim, git, mercurial, svn, MATLAB, SolidWorks, Multisim, Django, MPLAB, Labview, Eagle PCB}
	\resitem{\textbf{Office Software:} Microsoft Office, OpenOffice, \LaTeX}
	%\resitem{\textbf{General Software:} Microsoft Windows, Linux, Microsoft Office, OpenOffice, \LaTeX}
	%\resitem{\textbf{Numerical Simulation:} FORTRAN, MATLAB}
	%\resitem{\textbf{Lab Equipment:} Gilbert Technologies Furnace, Cobilt CA-400 Photomask Aligner, Sputtered Films S-Gun Sputtering System, Probe Station}
\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%

\begin{ressection}{Activities}
	
\ressubitem{Eagle Scout}

\end{ressection}

%%%%%%%%%%%%%%%%%%%%%%%%

\end{document}
